Privacy-Respecting Type Error Telemetry at Scale

### 2023-09-30 programming23/paper.tex
fix resolution, fig 5
sec 6

One way to futher strengthen the privacy of any telemetry design, including
transparent telemetry, is to systematically add noise to the data using
techniques from differential
privacy~\cite{zhlbr-cc-2020,epk-ccs-2014,wblj-usenix-2017}.
Recent work that is especially relevant to the session-based data collected
by Roblox Studio shows how to add noise to traces~\cite{zhlbr-cc-2020},
how to account for known relationships between events~\cite{zhlbr-oopsla-2020},
and how to choose the noise amount on the client side~\cite{hlzbr-ecoop-2021}.
Applying differential privacy is subtle, however.
While we can likely fuzz the total number of type errors, if we were to
fuzz the number of \code{CodeTooComplex} errors, it might drastically
affect our conclusions.

@@

Our approach to data analysis is inspired by Marceau
et~al.~\cite{mfk-onward-2011,mfk-sigcse-2011} and
Macedo et~al.~\cite{mcpcsprs-abz-2020,mcpcsprs-scp-2021}
for Racket and Alloy4Fun, respectively. Other more recent work has
also studied edit sequences to infer intent~\cite{wk-koli-2020,lgk-pj-2022,rsgl-cpp-2020}.
A major difference is that we have only samples, not full sequences,
which significantly impacts our study methods.

The BitFit project collects data about beginning students interactions in
Java~\cite{ekc-wccce-2016,anna-russo-kennedy-ms-2006}.
It does not collect source code, nor does it collect error messages;
the telemetry simply counts all (i.e., without sampling) compile events, hint
requests, etc. in a transparent~\cite{transparent-telemetry} manner.
Other logging-based studies of Java programs use the full error message to
draw conclusions~\cite{bgimgm-cse-2016,dlc-iticse-2014}, which we
cannot use to preserve privacy.

>>>>

One way to futher strengthen the privacy of any telemetry design, including
transparent telemetry, is to systematically add noise to the data using
techniques from differential
privacy~\cite{zhlbr-cc-2020,epk-ccs-2014,wblj-usenix-2017}.
Recent work about session-based data that could be added
to Roblox Studio shows how to add noise to traces~\cite{zhlbr-cc-2020},
how to account for known relationships between events~\cite{zhlbr-oopsla-2020},
and how to choose the noise on the client side~\cite{hlzbr-ecoop-2021}.
Applying differential privacy is subtle, however.
While we could fuzz the total number of type errors, if we were to
fuzz the number of \code{CodeTooComplex} errors, it might drastically
affect our inferences.

@@

Our approach to data analysis is inspired by Marceau
et~al.~\cite{mfk-onward-2011,mfk-sigcse-2011} and
Macedo et~al.~\cite{mcpcsprs-abz-2020,mcpcsprs-scp-2021}
for Racket and Alloy4Fun, respectively. Other more recent work has
also studied edit sequences to infer intent~\cite{wk-koli-2020,lgk-pj-2022,rsgl-cpp-2020}.
A major difference is that we have only samples, not full sequences,
which significantly impacts our study methods and inferences.

The BitFit project collects data about beginning students interactions in
Java~\cite{ekc-wccce-2016,anna-russo-kennedy-ms-2006}.
It does not collect source code, nor does it collect error messages;
the telemetry simply counts all (i.e., without sampling) compile events, hint
requests, etc. While it does operate in a
transparent~\cite{transparent-telemetry} manner, it only provides
coarse-grained information that would be insufficient in our study.
Other logging-based studies of Java programs use the full error message to
draw conclusions~\cite{bgimgm-cse-2016,dlc-iticse-2014}, which we
cannot use.
